$Z^\prime$ mass limits and the naturalness of supersymmetry

### 2015-03-06 paper/e6ssm-tuning-paper.tex
deleted empty Fine Tuning section, merged Numerical section into results since it was too short to justify heading.

\section{\label{sec:tuning}Fine Tuning}

@@

\section{\label{sec:numericalprocedure}Numerical Procedure}
Using the approach outlined above, we are able to scan the low energy
parameter space of the MSSM and E$_6$SSM and calculate the fine tuning
in each. To do so, we implemented the above expressions for computing
the fine tuning in a modified version of the E$_6$SSM spectrum
generator that was used in \cite{Athron:2013ipa}. This code
implemented two-loop RGEs for all parameters except the soft scalar
masses. In order to properly include the fine tuning impact of the
$SU(3)$ gaugino soft mass $M_3$, we have extended the original code to
make use of the two-loop RGEs generated by SARAH
\cite{Staub:2009bi,Staub:2010jh,Staub:2012pb,Staub:2013tta} and
FlexibleSUSY \cite{Athron:2014yba}, which also makes use of SOFTSUSY \cite{Allanach:2001kg,Allanach:2013kza}. The CP-even Higgs masses are
calculated including the leading one-loop effective potential
contributions given in \cite{Athron:2009bs} and the leading two-loop
contributions. To scan over the MSSM parameter space, the equivalent
MSSM fine tuning expressions were implemented into a modified version
of SOFTSUSY 3.3.10 \cite{Allanach:2001kg}. For
consistency with the results produced in the $E_6$ models, and for
computational speed, for our main scans only the dominant one- and
two-loop corrections to the CP-even Higgs masses were
included. Finally, in all of the results below the fine tuning was
evaluated at the scale
$Q=M_{\textrm{SUSY}}=\sqrt{m_{\tilde{t}_1}m_{\tilde{t}_2}}$, where
$m_{\tilde{t}_{1,2}}$ are the running $\overline{\textrm{DR}}$ stop
masses evaluated at $Q=M_{\textrm{SUSY}}$.

\section{\label{sec:results}Results}
% Our results. Plots to go in here:
%    - tuning as a function of stop mass for the MSSM and E6SSM
As discussed in the introduction many recent papers interested in
natural supersymmetry have focussed on light stops, with much
theoretical effort to find models where it is easier to get a $125$
GeV Higgs boson and light stops simultaneously and much experimental
efforts to search for light stops.  This is entirely appropriate since
there are many good reasons to expect the soft masses to be set at
high energies.  However that is not the only possibility and the fine
tuning problem depends strongly on the RG evolution from the GUT
scale, as the soft Higgs masses that appear in the EWSB conditions
pick up contributions from the soft squark masses.

>>>>

%% \section{\label{sec:tuning}Fine Tuning}

@@

%%\section{\label{sec:numericalprocedure}Numerical Procedure}

\section{\label{sec:results}Results}

Using the approach outlined above, we are able to scan the low energy
parameter space of the MSSM and E$_6$SSM and calculate the fine tuning
in each. To do so, we implemented the above expressions for computing
the fine tuning in a modified version of the E$_6$SSM spectrum
generator that was used in \cite{Athron:2013ipa}. This code
implemented two-loop RGEs for all parameters except the soft scalar
masses. In order to properly include the fine tuning impact of the
$SU(3)$ gaugino soft mass $M_3$, we have extended the original code to
make use of the two-loop RGEs generated by SARAH
\cite{Staub:2009bi,Staub:2010jh,Staub:2012pb,Staub:2013tta} and
FlexibleSUSY \cite{Athron:2014yba}, which also makes use of SOFTSUSY \cite{Allanach:2001kg,Allanach:2013kza}. The CP-even Higgs masses are
calculated including the leading one-loop effective potential
contributions given in \cite{Athron:2009bs} and the leading two-loop
contributions. To scan over the MSSM parameter space, the equivalent
MSSM fine tuning expressions were implemented into a modified version
of SOFTSUSY 3.3.10 \cite{Allanach:2001kg}. For
consistency with the results produced in the $E_6$ models, and for
computational speed, for our main scans only the dominant one- and
two-loop corrections to the CP-even Higgs masses were
included. Finally, in all of the results below the fine tuning was
evaluated at the scale
$Q=M_{\textrm{SUSY}}=\sqrt{m_{\tilde{t}_1}m_{\tilde{t}_2}}$, where
$m_{\tilde{t}_{1,2}}$ are the running $\overline{\textrm{DR}}$ stop
masses evaluated at $Q=M_{\textrm{SUSY}}$.

% Our results. Plots to go in here:
%    - tuning as a function of stop mass for the MSSM and E6SSM
As discussed in the introduction many recent papers interested in
natural supersymmetry have focussed on light stops, with much
theoretical effort to find models where it is easier to get a $125$
GeV Higgs boson and light stops simultaneously and much experimental
efforts to search for light stops.  This is entirely appropriate since
there are many good reasons to expect the soft masses to be set at
high energies.  However that is not the only possibility and the fine
tuning problem depends strongly on the RG evolution from the GUT
scale, as the soft Higgs masses that appear in the EWSB conditions
pick up contributions from the soft squark masses.
